A general and efficient representation of Ancestral Recombination Graphs

### 2023-09-22 paper.tex

[NOTE This is a pedantic and slightly bullshitty to end up on,
just writing it down to see if it works. Should probably cut.]
A final point to note, is that
if we are using the term ARG
to loosely refer to genetic genealogies of varying
levels of detail, either inferred or simulated,
it makes little sense to refer ``the'' Ancestral Recombination
Graph (i.e, in  the singular, like ``the tree'' or
``the phylogeny'')
% TODO add more if we keep this
as favoured by some~\citep[e.g.][]{
arenas2013importance,palamara2016argon,hubisz2020inference}.
While there is of course a single ``true'' ARG that describes
the actual history of a sample, in reality there will be astronically
many ARGs that are compatible with the data, even under
parsimony conditions or when sampling from a model.
There are many different levels of granularity at which we
can reason about recombination, and many different ARGs.
We should embrace this diversity.

>>>>

[NOTE This is a pedantic and slightly bullshitty to end up on,
just writing it down to see if it works. Should probably cut.]
A final point to note, is that
if we are using the term ARG
to loosely refer to genetic genealogies of varying
levels of detail, either inferred or simulated,
it makes little sense to refer ``the'' Ancestral Recombination
Graph (i.e, in  the singular, like ``the tree'' or
``the phylogeny'')
% TODO add more if we keep this
as favoured by some~\citep[e.g.][]{
arenas2013importance,palamara2016argon,hubisz2020inference}.
While there is of course a single ``true'' ARG that describes
the actual history of a sample, 
under parsimony conditions or when sampling from a model there 
will be astronomically
many ARGs that are equally likely given the data.
There are also many different levels of granularity at which we
can reason about recombination, 
and consequently many different types of ARG.
We should embrace this diversity.
